Adopting agile in the large: motivations, success factors and challenges

### 2014-04-28 journal/article.tex
Change resistance

@@

The problem of tension between management and development may also be opposite.
In cases where the change was emerging bottom up the reluctancy to change was
not in the team members but management.
This caused that significant organizational change could not be raised above the
team level. For instance, Atlas describes how it would have required executive
support to integrate the product management office and separate quality
assurance groups in the agile process [P3]. In this case, when managers owning
projects with many teams were not involved it retrained agile development to
spread beyond team level. Further, if management does not speak out a goal
towards using agile, developers feel that the agile methods may be replaced by
something else at any time [P12].
Lack middle management support was seen as the most serious shortcoming by
Spayd [P49]. Middle management is in a position to undermine the entire
transformation, and may do so if they do not participate in, and thus
understand, the agile method [P49].

@@

>>>>

The problem of tension between management and development may also be opposite.
In cases where the change was emerging bottom up the reluctancy to change was
not in the team members but management.
This caused that significant organizational change could not be raised above the
team level. For instance, Atlas describes how it would have required executive
support to integrate the product management office and separate quality
assurance groups in the agile process [P3]. In this case, when managers owning
projects with many teams were not involved it retrained agile development to
spread beyond team level. Further, if management does not speak out a goal
towards using agile, developers feel that the agile methods may be replaced by
something else at any time [P12].
Lack middle management support was seen as the most serious shortcoming by Spayd
[P49]. Middle management is in a position to undermine the entire
transformation, and may do so if they do not participate in, and thus
understand, the agile method. Agile brings changes to some management roles
[P2], and lack of understanding of agile development will leave managers feeling
left out [P6].

\subsubsection{Other organizational issues}

@@

@@

\subsubsection{Change resistance}

Change resistance is a central challenge in any organizational transformation.
People will not be willing to change unless there are good reasons, and the
change is preceived easy enough. It is difficult to attain a buy-in for a
change, and even organizations that have a flexible culture will face resistance
[P10]. It should be expected that not everyone will be willing to change, and
some employees will never adapt to the change [P6]. In one case it was reported
that objections from team members was a major reason for loss in time and
productivity [P29].

On a team level numoerous reasons for change resistance were given. For
instance, Fecarotta described the organization of Boeing as risk-averse and
cautious which slows down any change [P14]. The organization was also described
having a deeply rooted status-quo because of high employee retention, which
further hindered change. In some cases it was reported that people worried about
new roles and responsibilities that agile would possibly bring [P44]. For
instance, testers were worried that they would need to take on cross functional
tasks, which would be outside their area of expertise [P18]. Yet another reason
for change resistance was the move from own offices to team areas [P22]. People
were also feeling being monitored because of the increased level of interaction
within the team and between project stakeholders [P45].
One study reported the cultural change required by middle management as the
biggest cause of resistance [P2].

Change resistance was mitigated for instance by education [P45], and one-to-one
discussions [P22]. Change resistance was also softened by using first only teams
willing to try agile, so that insights could be gathered to ease the continued
transformation [P45].

% General -->

% For instance, teams may not be willing to try
% new approaches unless they have been proven [P6].

% Resistance is to be expected --> there are many different stakeholders [P41]
